---
title: "Homework1"
author: "Junzhe Shao"
date: "9/25/2021"
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```
# Problem 1
Starting with creating a example data frame: 
```{r Problem 1}
set.seed(123)

example_df = tibble(
  vec_random_sample = rnorm(10),
  vec_char = c("a","b","c","d","e","f","g","h","i","j"),
  vec_logical = vec_random_sample > 0,
  vec_factor = factor(c("A","B","A","A","C","A","C","B","B","A"))
)

example_df

```
Take the mean of each variable, and we have:
```{r}
mean(pull(example_df, var = vec_random_sample))
mean(pull(example_df, var = vec_char))
mean(pull(example_df, var = vec_logical))
mean(pull(example_df, var = vec_factor))
```
We can notice mean function can not applied with character or double.

Try with `r as.numeric()` function for logical, character, and factor
```{r eval=FALSE}
as.numeric(pull(example_df, var = vec_char))
as.numeric(pull(example_df, var = vec_logical))
as.numeric(pull(example_df, var = vec_factor))
```
We discovered that factor and logic can be transformed to be numeric type. They both "embedded" with a numeric variable under a rule which can introduce convenience for practical programming, for instance, the mean value of a logic vector is the percentage of TRUE value.Therefore they can be operated by mean function just as a numeric vector. I suppose this is a Syntactic sugar for basic data struture of R.  

# Problem 2
```{r}
data("penguins", package = "palmerpenguins")
as_tibble(penguins)
```
Discription of penguins data with in line R code:   

There are `r length(names(penguins))` variables which are `r names(penguins)`. The type of the variables are listed above as tibble.


The scatter plot with species: 
```{r}
ggplot(penguins, aes(y = flipper_length_mm, x = bill_length_mm, color = species)) + geom_point()
```

